---
title: "Experiment plots"
output: html_document
date: "2023-09-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev = "png",
                      dpi = 300,
                      cache = FALSE,
                      fig.dim = c(7, 4),
                      fig.align = "centre")

library(here)
library(tidyverse)
library(data.table)
library(ggplot2)
```


```{r}
data_df <- read_csv(file=here("Outputs", "logistic", "confidence_interval_ll_calls_algos.csv"))
algo_df <- read_csv(file=here("Outputs", "logistic", "algos.csv"))

data_df_means <- data_df %>% 
  arrange(algo_key, parameter) %>%
  group_by(parameter) %>%
  mutate(opt_rank =rank(optimisation_calls, ties.method ='min'), like_rank =rank(likelihood_calls, ties.method ='min')) %>%
  group_by(algo_key) %>%
  mutate(mean_opt_rank=mean(opt_rank), mean_like_rank=mean(like_rank), mean_opt_calls=mean(optimisation_calls), mean_ll_calls=mean(likelihood_calls)) %>%
  arrange(desc(-mean_like_rank)) %>%
  ungroup()


data_df %>% left_join(algo_df) %>% 
  select(-algo_key) %>%
  arrange(parameter, likelihood_calls, optimisation_calls) %>%
  group_by(parameter) %>%
  mutate(opt_rank =rank(optimisation_calls, ties.method ='min'), like_rank =rank(likelihood_calls, ties.method ='min')) %>%
  ungroup() %>%
  select(parameter, algo_name, likelihood_calls, like_rank, optimisation_calls, opt_rank) %>%
  write_csv(file=here("Outputs", "logistic", "algos_parameters.csv"))
  

data_df_means %>% left_join(algo_df) %>% 
  select(algo_name, mean_like_rank, mean_ll_calls, mean_opt_rank, mean_opt_calls) %>%
  unique() %>%
  mutate_if(is.numeric, signif, digits=3) %>%
  write_csv(file=here("Outputs", "logistic", "algos_mean.csv"))
```

```{r}
data_df <- read_csv(file=here("Outputs", "STAT5", "confidence_interval_ll_calls_algos.csv"))

data_df_means <- data_df %>% 
  arrange(algo_key, parameter) %>%
  group_by(parameter) %>%
  mutate(opt_rank =rank(optimisation_calls, ties.method ='min'), like_rank =rank(likelihood_calls, ties.method ='min')) %>%
  group_by(algo_key) %>%
  mutate(mean_opt_rank=mean(opt_rank), mean_like_rank=mean(like_rank), mean_opt_calls=mean(optimisation_calls), mean_ll_calls=mean(likelihood_calls)) %>%
  arrange(desc(-mean_like_rank)) %>%
  ungroup()


data_df %>% left_join(algo_df) %>% 
  select(-algo_key) %>%
  arrange(parameter, likelihood_calls, optimisation_calls) %>%
  group_by(parameter) %>%
  mutate(opt_rank =rank(optimisation_calls, ties.method ='min'), like_rank =rank(likelihood_calls, ties.method ='min')) %>%
  ungroup() %>%
  select(parameter, algo_name, likelihood_calls, like_rank, optimisation_calls, opt_rank) %>%
  write_csv(file=here("Outputs", "STAT5", "algos_parameters.csv"))
  

data_df_means %>% left_join(algo_df) %>% 
  select(algo_name, mean_like_rank, mean_ll_calls, mean_opt_rank, mean_opt_calls) %>%
  unique() %>%
  mutate_if(is.numeric, signif, digits=3) %>%
  write_csv(file=here("Outputs", "STAT5", "algos_mean.csv"))
```

Increasing find_zero_atol strictly decreases the number of LL evaluations because it strictly decreases the number of optimisation calls. This occurs after around 1e-14.
Increasing opt_abstol decreases the number of LL evaluations in general. However, if it gets too high then the optimiser will not find the true profile ll at each location and resultantly the number of optimisation calls may increase, either increasing the number of LL evaluations or making the magnitude of the decrease smaller.

```{r}
data_df <- read_csv(file=here("Outputs", "logistic", "confidence_interval_ll_calls.csv"))
data_df$parameter = as.factor(data_df$parameter)

data_df %>% filter(find_zero_atol==0.0) %>% 
  ggplot(aes(x=opt_abstol, y=likelihood_calls)) + 
  geom_point(aes(colour=parameter)) +
  scale_x_continuous(trans="log10") +
  theme_classic()+   
  theme(panel.grid.minor.y = element_line(size=0.1, color="grey"),     
        panel.grid.minor.x = element_line(size=0.1, color="grey"))


data_df %>% filter(find_zero_atol==0.0) %>% 
  ggplot(aes(x=opt_abstol, y=optimisation_calls)) + 
  geom_point(aes(colour=parameter)) +
  scale_x_continuous(trans="log10") +
  theme_classic()+   
  theme(panel.grid.minor.y = element_line(size=0.1, color="grey"),     
        panel.grid.minor.x = element_line(size=0.1, color="grey"))

data_df %>% filter(opt_abstol==0.0) %>% 
  ggplot(aes(x=find_zero_atol, y=likelihood_calls)) + 
  geom_point(aes(colour=parameter)) +
  scale_x_continuous(trans="log10") +
  theme_classic()+   
  theme(panel.grid.minor.y = element_line(size=0.1, color="grey"),     
        panel.grid.minor.x = element_line(size=0.1, color="grey"))

data_df %>% filter(opt_abstol==0.0) %>% 
  ggplot(aes(x=find_zero_atol, y=optimisation_calls)) + 
  geom_point(aes(colour=parameter)) +
  scale_x_continuous(trans="log10") +
  theme_classic()+   
  theme(panel.grid.minor.y = element_line(size=0.1, color="grey"),     
        panel.grid.minor.x = element_line(size=0.1, color="grey"))

data_df$find_zero_atol = as.factor(data_df$find_zero_atol)

data_df %>%
  ggplot(aes(x=opt_abstol, y=likelihood_calls)) + 
  geom_line(aes(colour=find_zero_atol)) +
  facet_wrap(~parameter,ncol=1, scales = "free_y")+
  scale_x_continuous(trans="log10") +
  theme_classic()+   
  theme(panel.grid.minor.y = element_line(size=0.1, color="grey"),     
        panel.grid.minor.x = element_line(size=0.1, color="grey"))

```   

```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
output_location = joinpath("Outputs", "logistic")
data_df = CSV.read(joinpath(output_location, "confidence_interval_ll_calls.csv"), DataFrame);
data_df_zero = filter(row -> row.find_zero_atol == 0.0, data_df)

format=(palette=:Paired, msw=0, size=(430,430), dpi=300, title="")

plt1 = @df data_df_zero scatter(log10.(:opt_abstol), :likelihood_calls; group=:parameter, alpha=0.8, legend_position=:topright, format... );
# ylabel!("Total Likelihood Calls")
# savefig(plt, joinpath(output_location, "conf_int_likelihood_calls_vs_abstol.pdf"))

plt2 = @df data_df_zero scatter(log10.(:opt_abstol), :optimisation_calls; group=:parameter, alpha=0.8, legend_position=nothing, format... );
xlabel!(L"log_{10}(\texttt{abstol})");
# ylabel!("Total Optimisation Calls\n")

plt=plot(plt1, plt2, layout=grid(2,1))
savefig(plt, joinpath(output_location, "conf_int_calls_vs_abstol.pdf"))


data_df_zero = filter(row -> row.opt_abstol == 0.0, data_df);

plt1 = @df data_df_zero scatter(log10.(:find_zero_atol), :likelihood_calls; group=:parameter, alpha=0.8, legend_position=nothing, format... );
# xlabel!(L"log_{10}(\texttt{atol})")
ylabel!("Total Likelihood Calls")
# savefig(plt, joinpath(output_location, "conf_int_likelihood_calls_vs_atol.pdf"))

plt2 = @df data_df_zero scatter(log10.(:find_zero_atol), :optimisation_calls; group=:parameter, alpha=0.8, legend_position=nothing, format... );
xlabel!(L"log_{10}(\texttt{atol})");
ylabel!("Total Optimisation Calls\n")
# savefig(plt, joinpath(output_location, "conf_int_optimisation_calls_vs_atol.pdf"))


plt=plot(plt1, plt2, layout=grid(2,1))
savefig(plt, joinpath(output_location, "conf_int_calls_vs_atol.pdf"))
  # ggplot(aes(x=opt_abstol, y=likelihood_calls)) + 
  # geom_point(aes(colour=parameter)) +
  # scale_x_continuous(trans="log10") +

```

```{r}
data_df <- read_csv(file=here("Outputs", "logistic", "confidence_interval_ll_calls_lower_and_upper.csv"))
if (is.null(data_df$name)){
  data_df = data_df %>% mutate(name=case_when(lower_found==F & upper_found==F ~ "Baseline",
                                  lower_found==T & upper_found==F ~ "Lower",
                                  lower_found==F & upper_found==T ~ "Higher",
                                  lower_found==T & upper_found==T ~ "Lower and Higher"))
  write_csv(data_df, file=here("Outputs", "logistic", "confidence_interval_ll_calls_lower_and_upper.csv"))
}
```

```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
output_location = joinpath("Outputs", "logistic")
data_df = CSV.read(joinpath(output_location, "confidence_interval_ll_calls_lower_and_upper.csv"), DataFrame);


format=(palette=:Paired, msw=0, size=(430,430), dpi=300, title="");

using CategoricalArrays
par_names = ["λ", "K", "C0"]
data_df.par_str = categorical(par_names[data_df.parameter], levels=par_names)

data_df.name_cat .= categorical(data_df.name; levels= ["Baseline", "Lower", "Higher", "Lower and Higher"])

plt1 = @df data_df groupedbar(:par_str, :likelihood_calls; bar_position=:dodge, group=:name_cat, legend_position=nothing, format...);
ylabel!("Total Likelihood Calls")

plt2 = @df data_df groupedbar(:par_str, :optimisation_calls; bar_position=:dodge, group=:name_cat, legend_position=:bottomright, format...);
ylabel!("Total Optimisation Calls")

savefig(plt1, joinpath(output_location, "conf_int_like_calls_vs_lu.pdf"))
savefig(plt2, joinpath(output_location, "conf_int_opt_calls_vs_lu.pdf"))
```

# Coverage outputs

## Parameter Confidence Intervals
```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
using CategoricalArrays

format=(msw=1.5, size=(500,400), dpi=300, title="", legend_position=nothing, ylabel="Simulated Coverage");
locs = ["logistic", "lotka_volterra", "logistic_twospecies"]

loc = locs[1]
output_location = joinpath("Outputs", loc)
data_df = CSV.read(joinpath(output_location, "univariate_parameter_coverage.csv"), DataFrame);
# data_df.θname = categorical(data_df.θname, levels=data_df.θname)

plt = @df data_df plot(:θname, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], ylimits=(0.8, 1.0),yticks=LinRange(0.8,1.0,5),
                        yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);
annotate!(data_df.θname, fill(0.8,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))


savefig(plt, joinpath(output_location, "univariate_parameter_coverage_"*loc*".pdf"))

loc = locs[2]
output_location = joinpath("Outputs", loc)
data_df = CSV.read(joinpath(output_location, "univariate_parameter_coverage.csv"), DataFrame);
# data_df.θname = categorical(data_df.θname, levels=data_df.θname)

plt = @df data_df plot(:θname, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], bar_position=:stack, ylimits=(0.8, 1.0), yticks=LinRange(0.8,1.0,5),
                        yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);
annotate!(data_df.θname, fill(0.8,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))

savefig(plt, joinpath(output_location, "univariate_parameter_coverage_"*loc*".pdf"))

loc = locs[3]
output_location = joinpath("Outputs", loc)
data_df = CSV.read(joinpath(output_location, "univariate_parameter_coverage.csv"), DataFrame);
# data_df.θname = categorical(data_df.θname, levels=data_df.θname)

plt = @df data_df plot(:θname, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], bar_position=:stack, ylimits=(0.6, 1.0), yticks=LinRange(0.6,1.0,9),
                        yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);

annotate!(data_df.θname, fill(0.6,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))
savefig(plt, joinpath(output_location, "univariate_parameter_coverage_"*loc*".pdf"))

output_location = joinpath("Outputs", loc)
data_df = CSV.read(joinpath(output_location, "univariate_parameter_coverage_more_data.csv"), DataFrame);
# data_df.θname = categorical(data_df.θname, levels=data_df.θname)

plt = @df data_df plot(:θname, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], bar_position=:stack, ylimits=(0.6, 1.0), yticks=LinRange(0.6,1.0,9),
                        yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);

annotate!(data_df.θname, fill(0.6,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))

display(data_df)
savefig(plt, joinpath(output_location, "univariate_parameter_coverage_"*loc*"_more_data.pdf"))
```

## True Bivariate Boundary
### Logistic example

Focusing on 95% lower quantile performance, i.e. in 95% of cases it will be at least 'this' good.
```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
using CategoricalArrays

format=(palette=:seaborn_colorblind, lw=2, size=(500,400), dpi=300, title="", msw=0, mw=4, legend_position=:bottomright, xlabel="Total Boundary Points", minorgrid=true, minorticks=2, yticks=0.1:0.1:1.0, ylims=(0.2, 1.0));
locs = ["logistic", "lotka_volterra", "logistic_twospecies"];

loc = locs[1];
output_location = joinpath("Outputs", loc);
data_df = CSV.read(joinpath(output_location, "bivariate_boundary_coverage.csv"), DataFrame);

method_df = CSV.read(joinpath(output_location, "methods.csv"), DataFrame);
method_df[:, :method_name] .= [split(name, "(")[1] for name in method_df.method_name];
method_df[end, :method_name] = "IterativeBoundary_RadialRandom"
data_df[:, :hullmethod] .= [split(name, "(")[1] for name in data_df.hullmethod];

data_df = leftjoin(data_df, method_df, on=:method_key);

data_df.method_name = categorical(data_df.method_name, levels=["Fix1AxisMethod", "SimultaneousMethod", "RadialRandomMethod", "RadialMLEMethod", "IterativeBoundaryMethod", "IterativeBoundary_RadialRandom"])

plots = []
for sub_df in groupby(data_df, [:hullmethod, :θindices])
  plt = @df sub_df plot(:num_points, :coverage_median; group=:method_name, marker=(:circle), ylabel="Simulated Area Coverage (0.50 Quantile)", format...)
  hline!(plt, [0.98], linestyle=:dash, label="98%", color=:black)
  plt.subplots[1].series_list = [plt.subplots[1].series_list[end]; plt.subplots[1].series_list[1:end-1]]
  push!(plots, plt)
end

display(plots[1])
display(plots[2])
display(plots[3])
display(plots[4])
display(plots[5])
display(plots[6])

plots = []
for sub_df in groupby(data_df, [:hullmethod, :θindices])
  plt = @df sub_df plot(:num_points, :coverage_lb; group=:method_name, marker=(:circle), ylabel="Simulated Area Coverage", format...)
  hline!(plt, [0.98], linestyle=:dash, label="98%", color=:black)
  plt.subplots[1].series_list = [plt.subplots[1].series_list[end]; plt.subplots[1].series_list[1:end-1]]
  push!(plots, plt)
end

for i in eachindex(plots)
  plot!(plots[i],size=(400,400))
  if (((i-1) % 3)+1) != 1; plot!(plots[i], legend_position=nothing) end
  
  hullmethod =  i < 4 ? "_MPP_" : "_ConvexHull_" 
  
  savefig(plots[i], joinpath(output_location, "bivariate_area_coverage"* hullmethod *string(((i-1)%3)+1)*".pdf"))
end

display(plots[1])
display(plots[2])
display(plots[3])
display(plots[4])
display(plots[5])
display(plots[6])





format=(palette=:seaborn_colorblind, lw=2, size=(500,400), dpi=100, title="", legend_position=:bottomright, 
        # xlabel="Total Boundary Points", minorgrid=true, minorticks=2, 
        yticks=00:10:100
        );


pnts_to_reach_coverage_df = DataFrame(method_name=String[], hullmethod=String[], θindices=String[], quantile=Float64[], coverage_level=String[], num_points=Int[])
coverage_levels=[0.97, 0.98, 0.99]

for sub_df in groupby(data_df, [:method_name, :hullmethod, :θindices])

  for level in coverage_levels
    i = findfirst(sub_df.coverage_median .>= level)
    dfrow = [sub_df.method_name[1], sub_df.hullmethod[1], sub_df.θindices[1], 0.5, string(level), -10]  
    if isnothing(i)
      push!(pnts_to_reach_coverage_df, dfrow)
    else
      dfrow[end] = sub_df[i, :num_points]
      push!(pnts_to_reach_coverage_df, dfrow)
    end
  end

end

for sub_df in groupby(data_df, [:method_name, :hullmethod, :θindices])

  for level in coverage_levels
    i = findfirst(sub_df.coverage_lb .>= level)
    dfrow = [sub_df.method_name[1], sub_df.hullmethod[1], sub_df.θindices[1], 0.05, string(level), -10]  
    if isnothing(i)
      push!(pnts_to_reach_coverage_df, dfrow)
    else
      dfrow[end] = sub_df[i, :num_points]
      push!(pnts_to_reach_coverage_df, dfrow)
    end
  end

end

pnts_to_reach_coverage_df.coverage_level = categorical(pnts_to_reach_coverage_df.coverage_level, levels=string.(coverage_levels))
pnts_to_reach_coverage_df.method_name = categorical(pnts_to_reach_coverage_df.method_name, levels=["Fix1AxisMethod", "SimultaneousMethod", "RadialRandomMethod", "RadialMLEMethod", "IterativeBoundaryMethod", "IterativeBoundary_RadialRandom"])


pnts_to_reach_wide = unstack(pnts_to_reach_coverage_df, [:θindices, :method_name, :hullmethod, :quantile], :coverage_level, :num_points)
sort!(pnts_to_reach_wide, [:quantile, :θindices, :method_name])

CSV.write(joinpath(output_location, "pnts_to_reach_coverage.csv"), pnts_to_reach_wide);

```

```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
using CategoricalArrays

format=(palette=:seaborn_colorblind, lw=2, size=(500,400), dpi=300, title="",  msw=0, mw=4, legend_position=:topleft, xlabel="Total Boundary Points",  minorgrid=true, minorticks=2, #yticks=0.1:0.1:1.0
        opacity=0.8,
        );
locs = ["logistic", "lotka_volterra", "logistic_twospecies"];

loc = locs[1];
output_location = joinpath("Outputs", loc);
data_df = CSV.read(joinpath(output_location, "confidence_boundary_ll_calls.csv"), DataFrame);

method_df = CSV.read(joinpath(output_location, "methods.csv"), DataFrame);
method_df[:, :method_name] .= [split(name, "(")[1] for name in method_df.method_name];
method_df[end, :method_name] = "IterativeBoundary_RadialRandom"

data_df = leftjoin(data_df, method_df, on=:method_key);

data_df.method_name = categorical(data_df.method_name, levels=["Fix1AxisMethod", "SimultaneousMethod", "RadialRandomMethod", "RadialMLEMethod", "IterativeBoundaryMethod", "IterativeBoundary_RadialRandom"]);


data_gdf = groupby(data_df, [:method_name, :num_points])
data_mean_opt = combine(data_gdf, :optimisation_calls=>mean, :likelihood_calls=>mean)

data_mean_opt.method_name = categorical(data_mean_opt.method_name, levels=["Fix1AxisMethod", "SimultaneousMethod", "RadialRandomMethod", "RadialMLEMethod", "IterativeBoundaryMethod", "IterativeBoundary_RadialRandom"]);

plt = @df data_mean_opt plot(:num_points, :optimisation_calls_mean; marker=(:circle), group=:method_name, ylims=(0, 3000), ylabel="Mean Optimisation Calls",  format...)
savefig(plt, joinpath(output_location, "boundary_points_vs_opt_calls_mean.pdf"))

plt = @df data_mean_opt plot(:num_points, :likelihood_calls_mean; marker=(:circle), group=:method_name, ylabel="Mean Likelihood Calls", format...)
savefig(plt, joinpath(output_location, "boundary_points_vs_ll_calls_mean.pdf"))

plots = []
for sub_df in groupby(data_df, [:θindices])
  plt = plot()

  @df sub_df plot!(plt, :num_points, :optimisation_calls; marker=(:circle), group=:method_name, ylims=(0, 3000), ylabel="Mean Optimisation Calls", format...)
  push!(plots, plt)
end

for i in eachindex(plots)
  plot!(plots[i],size=(400,400))
  if i != 1; plot!(plots[i], legend_position=nothing) end
  
  savefig(plots[i], joinpath(output_location, "boundary_points_vs_opt_calls_"*string(i)*".pdf"))
end
```
50% wider bounds
```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
using CategoricalArrays

format=(palette=:seaborn_colorblind, lw=2, size=(500,400), dpi=300, title="",  msw=0, mw=4, legend_position=nothing, xlabel="Total Boundary Points", minorgrid=true, minorticks=2, #yticks=0.1:0.1:1.0
        opacity=0.8,
        );
locs = ["logistic", "lotka_volterra", "logistic_twospecies"];

loc = locs[1];
output_location = joinpath("Outputs", loc);
data_df = CSV.read(joinpath(output_location, "confidence_boundary_ll_calls_widerbounds.csv"), DataFrame);

method_df = CSV.read(joinpath(output_location, "methods.csv"), DataFrame);
method_df[:, :method_name] .= [split(name, "(")[1] for name in method_df.method_name];
method_df[end, :method_name] = "IterativeBoundary_RadialRandom"

data_df = leftjoin(data_df, method_df, on=:method_key);

data_df.method_name = categorical(data_df.method_name, levels=["Fix1AxisMethod", "SimultaneousMethod", "RadialRandomMethod", "RadialMLEMethod", "IterativeBoundaryMethod", "IterativeBoundary_RadialRandom"]);


data_gdf = groupby(data_df, [:method_name, :num_points])
data_mean_opt = combine(data_gdf, :optimisation_calls=>mean, :likelihood_calls=>mean)

data_mean_opt.method_name = categorical(data_mean_opt.method_name, levels=["Fix1AxisMethod", "SimultaneousMethod", "RadialRandomMethod", "RadialMLEMethod", "IterativeBoundaryMethod", "IterativeBoundary_RadialRandom"]);

plt = @df data_mean_opt plot(:num_points, :optimisation_calls_mean; marker=(:circle), group=:method_name, ylims=(0,3000), ylabel="Mean Optimisation Calls", format...)
savefig(plt, joinpath(output_location, "boundary_points_vs_opt_calls_widerbounds_mean.pdf"))

plt = @df data_mean_opt plot(:num_points, :likelihood_calls_mean; marker=(:circle), group=:method_name, ylabel="Mean Likelihood Calls", format...)
savefig(plt, joinpath(output_location, "boundary_points_vs_ll_calls_widerbounds_mean.pdf"))

plots = []
for sub_df in groupby(data_df, [:θindices])
  plt = plot()

  @df sub_df plot!(plt, :num_points, :optimisation_calls; marker=(:circle), group=:method_name,  ylims=(0,3000), ylabel="Mean Optimisation Calls", format...)
  push!(plots, plt)
end

for i in eachindex(plots)
  plot!(plots[i],size=(400,400))
  if i == 3; plot!(plots[i], legend_position=:topleft) end
  
  savefig(plots[i], joinpath(output_location, "boundary_points_vs_opt_calls_widerbounds_"*string(i)*".pdf"))
end


```

### Lotka-volterra example

```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
using CategoricalArrays

format=(palette=:seaborn_colorblind, lw=2, size=(500,400), dpi=300, title="", msw=0, mw=4, legend_position=:bottomright, xlabel="Total Boundary Points", minorgrid=true, minorticks=2, yticks=0.86:0.02:1.0, ylims=(0.86, 1.0));
locs = ["logistic", "lotka_volterra", "logistic_twospecies"];

loc = locs[2];
output_location = joinpath("Outputs", loc);
data_df = CSV.read(joinpath(output_location, "bivariate_boundary_coverage.csv"), DataFrame);

data_df[:, :hullmethod] .= [split(name, "(")[1] for name in data_df.hullmethod];

# θnames=["α", "β", "x0", "y0"]
# data_df.θnames2 = ["("*θnames[inds[1]] *", "*  θnames[inds[2]]*")" for inds in data_df.θindices)
data_df.θindices = categorical(data_df.θindices, levels=unique(data_df.θindices));


plots = []
for sub_df in groupby(data_df, [:hullmethod])
  plt = @df sub_df plot(:num_points, :coverage_lb; group=:θindices, marker=(:circle), ylabel="Simulated Area Coverage (0.05 Quantile)", format...)
  hline!(plt, [0.98], linestyle=:dash, label="98%", color=:black)
  plt.subplots[1].series_list = [plt.subplots[1].series_list[end]; plt.subplots[1].series_list[1:end-1]]
  push!(plots, plt)
end

display(plots[1])
display(plots[2])

savefig(plots[1], joinpath(output_location, "bivariate_area_coverage_MPP.pdf"))
savefig(plots[1], joinpath(output_location, "bivariate_area_coverage_ConvexHull.pdf"))

```

## Bivariate Confidence Profiles

```{julia}
using DataFrames, CSV
using Plots, StatsPlots; gr()
using LaTeXStrings
using CategoricalArrays

format=(msw=1.5, size=(500,400), dpi=300, title="", legend_position=nothing, ylabel="Simulated Coverage");
locs = ["logistic", "lotka_volterra", "logistic_twospecies"]

loc = locs[1]
output_location = joinpath("Outputs", loc)
data_df = CSV.read(joinpath(output_location, "bivariate_parameter_coverage.csv"), DataFrame);
# data_df.θname = categorical(data_df.θname, levels=data_df.θname)

plt = @df data_df plot(:θindices, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], ylimits=(0.8, 1.0),yticks=LinRange(0.8,1.0,5),
                        yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);
annotate!(data_df.θindices, fill(0.8,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))


savefig(plt, joinpath(output_location, "bivariate_parameter_coverage_"*loc*".pdf"))

loc = locs[2]
output_location = joinpath("Outputs", loc)
data_df = CSV.read(joinpath(output_location, "bivariate_parameter_coverage.csv"), DataFrame);
# data_df.θname = categorical(data_df.θname, levels=data_df.θname)

plt = @df data_df plot(:θindices, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], bar_position=:stack, ylimits=(0.8, 1.0), yticks=LinRange(0.8,1.0,5),
                        yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);
annotate!(data_df.θindices, fill(0.8,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))

savefig(plt, joinpath(output_location, "bivariate_parameter_coverage_"*loc*".pdf"))

# loc = locs[3]
# output_location = joinpath("Outputs", loc)
# data_df = CSV.read(joinpath(output_location, "bivariate_parameter_coverage.csv"), DataFrame);
# # data_df.θname = categorical(data_df.θname, levels=data_df.θname)
# 
# plt = @df data_df plot(:θname, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], bar_position=:stack, ylimits=(0.6, 1.0), yticks=LinRange(0.6,1.0,9),
#                         yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);
# 
# annotate!(data_df.θname, fill(0.6,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))
# savefig(plt, joinpath(output_location, "parameter_coverage_"*loc*".pdf"))
# 
# output_location = joinpath("Outputs", loc)
# data_df = CSV.read(joinpath(output_location, "bivariate_parameter_coverage_more_data.csv"), DataFrame);
# # data_df.θname = categorical(data_df.θname, levels=data_df.θname)
# 
# plt = @df data_df plot(:θname, :coverage; st=:bar, color=palette(:Paired)[1:nrow(data_df)], bar_position=:stack, ylimits=(0.6, 1.0), yticks=LinRange(0.6,1.0,9),
#                         yerror=(data_df.coverage .- data_df.coverage_lb, data_df.coverage_ub .- data_df.coverage), format...);
# 
# annotate!(data_df.θname, fill(0.6,nrow(data_df)), text.(data_df.coverage, fill(:bottom,nrow(data_df)), fill(:black,nrow(data_df)), fill(8,nrow(data_df))))
# 
# display(data_df)
# savefig(plt, joinpath(output_location, "bivariate_parameter_coverage_"*loc*"_more_data.pdf"))
```










